Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-07-07 doc/manuscript/manuscript.Rmd
add more context to intro
add statement about GAC in processing

In this study, we analyze and characterize the genetic and phenotypic diversity of 366 *S. sclerotiorum* isolates collected between 2003 and 2012 from dry bean cultivars among different geographic locations in the United States, France, Mexico, and Australia. 
Because the white mold nurseries serve as testing grounds for new varieties of dry bean, we wanted to know if the *S. sclerotiorum* populations from white mold nurseries were representative of the fields within the same region. 
As these nurseries are not treated with any chemical or cultural control of white mold, we hypothesized that these nurseries would represent the natural population of *S. sclerotiorum*.
Furthermore, as three cultivars (Beryl, Bunsi, and G122) were grown among all white mold nurseries, we wanted to investigate the potential effect of cultivar on genetic diversity.
We additionally wanted to assess what categorical or phenotypic variables best predict genetic structure and if there was correlation between multilocus genotype and mycelial compatibility group.

@@

Of the 16 microsatellite loci, five included compound repeats, which made allele scoring difficult. 
These loci were removed for the reported statistics, but were processed and included in data analyses to ensure the integrity of the results with 11 loci as compared to 16.
To control for non-independent samples (i.e. those sampled from the same location, region, year, and plant), data were clone-corrected for subsequent analyses.
The clone-corrected data set included 318 isolates.
All analyses were performed on this data set unless otherwise mentioned.
All data processing and analyses were performed in R version 3.4.0 [@R] and are openly available and reproducible at https://github.com/everhartlab/sclerotinia-366/

>>>>

In this study, we analyze and characterize the genetic and phenotypic diversity of 366 *S. sclerotiorum* isolates collected between 2003 and 2012 from dry bean cultivars among different geographic locations in the United States, France, Mexico, and Australia. 
Because the white mold nurseries serve as testing grounds for new varieties of dry bean, we wanted to know if the *S. sclerotiorum* populations from white mold nurseries were representative of the fields within the same region. 
As these nurseries are not treated with any chemical or cultural control of white mold, we hypothesized that these nurseries would represent the natural population of *S. sclerotiorum*.
Furthermore, as three cultivars (Beryl, Bunsi, and G122) were grown among all white mold nurseries, we wanted to investigate the potential effect of cultivar on genetic diversity.
We additionally wanted to assess what categorical or phenotypic variables best predict genetic structure and if there was correlation between multilocus genotype and mycelial compatibility group.
By investigating these aims, we hope to effectively describe the population dynamics of *S. sclerotiorum* and make available our database of isolates for use in future dry bean breeding efforts.

@@

Of the 16 microsatellite loci, five included compound repeats, which made allele scoring difficult. 
These loci were removed for the reported statistics, but were processed and included in data analyses to ensure the integrity of the results with 11 loci as compared to 16.
We assessed the power of our 11 markers by generating a genotype accumulation curve in the R package *poppr* version 2.4.1, looking for evidence of saturation, which would indicate that enough loci have been sampled to sufficiently characterize the full set of genotypes [@arnaud2007standardizing, @kamvar2015novel].
To control for non-independent samples (i.e. those sampled from the same location, region, year, and plant), data were clone-corrected for subsequent analyses.
The clone-corrected data set included 318 isolates.
All analyses were performed on this data set unless otherwise mentioned.
All data processing and analyses were performed in R version 3.4.0 [@R] and are openly available and reproducible at https://github.com/everhartlab/sclerotinia-366/
